Does Political Integration Make Cities Grow Faster?\\ Evidence From Dynastic Takeovers\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-02-23 paper/paper.tex
make paper look nice

\begin{document}
\maketitle

@@

Keep in mind that the title doesn't need to say everything. It needs to be catchy and it needs to be not-misleading about the core of the paper.
Alternative title ideas: 
\begin{itemize}
    \item "Good riddance? What happens to states when dynasties go extinct" - catchy, but obscure, and also not what the paper is about.
    \item "What kind of ruler makes states prosper?" "The best kind of autocrat?"
    \item ``Territory size, leaders and economic development: Evidence from German dynasties'' {Leaders, territory size and growth: Evidence from extinctions of German dynasties}

    \item "How individual dynasties in the HRE promoted or hindered growth" - to the point, but detached from literature.
    \item Dynastic Takeovers
    \item Extinctions of Noble Families
    \item Preview of results
    \item Which country you belong to / ``When cities change hands''
    \item {Extinctions of dynasties and changes in development}
    \item {When Cities Change Hands: Extinctions of Dynasties and Changes in Development} - very clean but also detached from literature (may be fine, though)
    \item Family Affair / Family Matters / Family Business / something more fitting about families
    \item Successions and success
    \item Power and prosperity
    \item {Family Matters: Extinctions of Dynasties and Changes in Development}
    \item something about game of thrones / a silly pun
    \item Adoptive Family / Foster Father or Evil Stepdad / In-laws
    \item Foster family or evil in-laws [only if many takeovers are by inlaws]
    \item ... of N German cities
    \item {When Cities Change Hands: Extinctions of Dynasties and \\Breaks in the Development of N German Cities}
    \item {State Size and City Growth: Evidence from Dynastic Takeovers}
    \item {Political Integration and Growth: \\Evidence from Dynastic Takeovers}
    \end{itemize}

@@

\setcounter{page}{1}

\doublespacing

@@

\newpage
\bibliographystyle{chicago}
\bibliography{references.bib}

>>>>

\begin{document}
\onehalfspacing
\maketitle
\thispagestyle{empty}

@@

@@

\setcounter{page}{1}
\doublespacing

@@

\newpage
\onehalfspacing
\bibliographystyle{chicago}
\bibliography{references.bib}
